Clustering Constraints on the Relative Sizes of Central and Satellite Galaxies

### 2017-11-13 paper/galsize_paper.tex
Updated Figure 1 with a scatter plot

%---------------------------------------------------------------------------------------------------
\begin{figure*}
\centering
\includegraphics[width=\textwidth]{FIGS/sdss_small_large_sample_definitions.pdf}
\caption{
{\bf Definition of ``small" and ``large" galaxies.} For a volume-limited SDSS galaxy sample defined by $M_{\ast}>10^{10.25}M_{\odot},$ we visually demonstrate how we classify galaxies into ``small" and ``large" subsamples. As described in detail in \S\ref{subsec:sizedef}, we compute the median value $\median{\rhalf}{\mstar}$ at the stellar mass of each galaxy in the sample, and divide the sample into two based on this $\mstar-$dependent cut. The {\em left panel} compares the stellar mass functions $\phi(\mstar)$ of the two samples, confirming that our method for separating ``small" from ``large" galaxies yields subsamples with statistically indistinguishable $\phi(\mstar)$. The {\em right panel} shows histograms of $\rhalf$ for the two subsamples, which partially overlap due to the stellar mass range spanned by the volume-limited, $\mstar$-threshold sample.
}
\label{fig:sizedefinition}
\end{figure*}
%-----------------------------------------------------------------------------------------------------

@@

Using this technique, for any $\mstar-$threshold sample, the stellar mass function of the ``large" and ``small" subsamples are identical. We illustrate this for the particular case of $\mstar>10^{10.25}\msun$ in left panel of Figure~\ref{fig:sizedefinition}, which shows stellar mass functions for the two subsamples. The right panel of Figure~\ref{fig:sizedefinition} compares histograms of the two size distributions of these subsamples, which partially overlap due to the variation in $\median{\rhalf}{\mstar}$ across the $\mstar-$ range of the threshold sample.

>>>>

%---------------------------------------------------------------------------------------------------
\begin{figure*}
\centering
\includegraphics[width=9cm]{FIGS/sdss_size_vs_mstar_scatter.pdf}
\includegraphics[width=\textwidth]{FIGS/sdss_small_large_sample_definitions.pdf}
\caption{
{\bf Definition of ``small" and ``large" galaxies.} For a volume-limited SDSS galaxy sample defined by $M_{\ast}>10^{10.25}M_{\odot},$ the {\em top panel} visually demonstrates how we classify galaxies into ``small" and ``large" subsamples. As described in detail in \S\ref{subsec:sizedef}, we compute the median value $\median{\rhalf}{\mstar}$ at the stellar mass of each galaxy in the sample, and divide the sample into two based on this $\mstar-$dependent cut. The {\em bottom left panel} compares the stellar mass functions $\phi(\mstar)$ of the two samples, confirming that our method for separating ``small" from ``large" galaxies yields subsamples with statistically indistinguishable $\phi(\mstar)$. The {\em bottom right panel} shows histograms of $\rhalf$ for the two subsamples, which partially overlap due to the stellar mass range spanned by the volume-limited, $\mstar$-threshold sample.
}
\label{fig:sizedefinition}
\end{figure*}
%-----------------------------------------------------------------------------------------------------

@@

Using this technique, for any $\mstar-$threshold sample, the stellar mass function of the ``large" and ``small" subsamples are identical. We illustrate this for the particular case of $\mstar>10^{10.25}\msun$ in bottom left panel of Figure~\ref{fig:sizedefinition}, which shows stellar mass functions for the two subsamples. The bottom right panel of Figure~\ref{fig:sizedefinition} compares histograms of the two size distributions of these subsamples, which partially overlap due to the variation in $\median{\rhalf}{\mstar}$ across the $\mstar-$ range of the threshold sample.
